### 2023-10-02 README.Rmd
updated tests
worfklow added 230925
updated rmd - 231002

<!-- badges: end -->

The goal of validateHOT is to validate the results of your validation
task (also known as holdout task). A validation task is essential to
make sure that your collected data of a MaxDiff, CBC, or ACBC are valid
and can also predict outside tasks that were not included in estimating
your utility scores. Although commercial studies often do not include a
validation/holdout task (Yang et al., 2018), it is highly recommended to do so
(Orme, 2015; Rao, 2014). This validation/holdout task does not only
help to check whether everything went right during data collection but
also to determine your final model. <code>validatHOT</code> provides
some of the relevant metrics to test the performance of your data in
predicting a holdout task. In [Sawtooth
Software's](https://sawtoothsoftware.com/) CBC a fixed validation/
holdout task is automatically implemented. If you conduct a MaxDiff or
ACBC study, you have to program these on your own.

@@

In the next step, we would like to see how well our model (from which we took the raw utilities) predict 
the actual choices in the validation/holdout task. First, we will test the <code>hitrate()</code> function. 
We specify the <code>data</code>, the column names of the alternatives (<code>opts</code>; remember 
we have three alternatives + the *no-buy* alternative), and finally the actual choice.

>>>>

[![R-CMD-check](https://github.com/JoshSchramm94/validateHOT/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JoshSchramm94/validateHOT/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of validateHOT is to validate the results of your validation
task (also known as holdout task). A validation task is essential to
make sure that your collected data of a MaxDiff, CBC, or ACBC are valid
and can also predict outside tasks that were not included in estimating
your utility scores. Although commercial studies often do not include a
validation/holdout task (Yang et al., 2018), it is highly recommended to do so
(Orme, 2015; Rao, 2014). This validation/holdout task does not only
help to check whether everything went right during data collection but
also to determine your final model. <code>validatHOT</code> provides
some of the relevant metrics to test the performance of your data in
predicting a holdout task. In [Sawtooth
Software's](https://sawtoothsoftware.com/) CBC a fixed validation/
holdout task is automatically implemented. If you conduct a MaxDiff or
ACBC study, you have to program these on your own. Since the start of

@@

In the next step, we would like to see how well our model (from which we took the raw utilities) predict 
the actual choices in the validation/holdout task. First, we will test the <code>hitrate()</code> function. 
We specify the <code>data</code>, the column names of the alternatives (<code>opts</code>; remember 
there are three alternatives + the *no-buy* alternative), and finally the actual choice.
